---
title: "test"
output: html_document
date: "2023-04-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usmap)
library(gplots)
```

```{r date functions and constants}
time_limit <- as.POSIXct("2016-08-05", format = "%Y-%m-%d", tz = "UTC")

get_time <- function(time) {
  return(as.POSIXct(time, format = "%Y-%m-%d %H:%M:%OS", tz = "UTC"))
}
```

```{r}
clients <- read.csv("../../clients.csv") %>%
  select(EthnicIdentity, ClientUno)

EthnicIdentity <- read.csv("../../EthnicIdentity.csv")

questionpostsprocessed <- read.csv("../../questionpostsprocessed.csv")

questions <- read.csv("../../questions.csv") %>% 
  filter(get_time(AskedOnUtc) > time_limit) %>%
  arrange(CategoryUno, QuestionUno) %>% 
  select(-c(CategoryUno, SubcategoryUno)) %>%
  mutate(AskedOnYear = year(get_time(AskedOnUtc)),
         AskedOnMonth = month(get_time(AskedOnUtc)),
         AskedOnMonthYear = (year(get_time(AskedOnUtc)) - 2016) * 12 + month(get_time(AskedOnUtc)),
         state = StateAbbr,
         AskedOnDay = day(get_time(AskedOnUtc)),
         AskedOnHour = hour(get_time(AskedOnUtc)),
         AskedOnWeekdays = weekdays(get_time(AskedOnUtc))
    )
```

### Top 10 Subcategories being Asked:
  Family/Divorce/Custody	
  Other	
  Family/Divorce/Custody/Adoption	
  Housing or Property Owned	
  Debts & Purchases	
  Family/Safety/Divorce/Custody	
  Family Law Questions	
  Civil/Constitutional Rights	
  Housing/Landlord Tenant/Eviction/Foreclosure or Property Owned	
  Housing or Real Estate

```{r}
questions %>%
  group_by(Subcategory) %>%
  summarize(
    nn = n()
  ) %>%
  arrange(-nn)
```

### Top Three Ethnicities of Clients: 

206490 (62.3%) of clients are identified as Caucasians, African American, and Latino/Hispanic. Caucasians has the biggest share (45%), followed by African American (11%) and Latino/Hispanic (8%). The actual values should be higher, given that 22% of the client prefer not to answer or has missing data for ethnic identity.

(Note: Some clients have more than 1 identity)

```{r}
EthnicIdentity
```


### Questions being asked across time
- Number of questions grows continuously, has a sharp increase in 2017 and 2020 
  - No significant change in topic asked in 2017
  - 35% of Work/Employment/Unemployment Question is asked in 2020 (Covid-19 Pandemic)
  
- Most questions are asked (indifferent of categories):
  In January and July - September
  No difference within days of a month
  on Tuesday, during working hours

```{r}
questions %>%
  filter(AskedOnYear == 2017) %>%
  group_by(Subcategory) %>%
  summarize(
    nn = n()
  ) %>%
  arrange(-nn)
```


```{r}
questions %>%
  group_by(AskedOnMonthYear, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnMonthYear, y = n, color = Category)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Months",
    y = "Number of Question"
  )

questions %>%
  group_by(AskedOnYear, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnYear, y = n, color = Category)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Year",
    y = "Number of Question"
  )

questions %>%
  group_by(AskedOnMonth, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnMonth, y = n, color = Category)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Months",
    y = "Number of Question"
  )

questions %>%
  group_by(AskedOnHour, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnHour, y = n, color = Category)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Hours",
    y = "Number of Question"
  )

questions %>%
  group_by(AskedOnDay, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnDay, y = n, color = Category)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Days",
    y = "Number of Question"
  )

# weekday_to_number <- function(weekday) {
#   switch(tolower(weekday),
#          "sunday" = 1,
#          "monday" = 2,
#          "tuesday" = 3,
#          "wednesday" = 4,
#          "thursday" = 5,
#          "friday" = 6,
#          "saturday" = 7)
# }

weekdays_to_numbers <- function(weekdays) {
  sapply(tolower(weekdays), function(weekday) {
    switch(weekday,
           "sunday" = 1,
           "monday" = 2,
           "tuesday" = 3,
           "wednesday" = 4,
           "thursday" = 5,
           "friday" = 6,
           "saturday" = 7)
  })
}

questions %>%
  ggplot(mapping = aes(x = weekdays_to_numbers(AskedOnWeekdays), fill = Category)) +
  geom_bar() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Days",
    y = "Number of Question"
  )

```

```{r}
questions %>%
  group_by(AskedOnMonth) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnMonth, y = n)) +
  geom_line() +
  labs(
    title = "Number of questions asked for each category",
    subtitle = "August 5, 2016 to 27 January 27, 2022",
    x = "Year",
    y = "Number of Question"
  )
```

US Map showing density of categories for each US state

```{r}
vector_of_category <- c("Family and Children", "Other", "Housing and Homelessness", "Consumer Financial Questions", "Individual Rights", "Income Maintenance", "Health and Disability", "Education", "Juvenile")

plot_map <- function(category) {
  subset <- questions %>%
    filter(Category == category) %>%
    group_by(state) %>%
    summarize(
      values = n(),
    )
  plot <- plot_usmap(data = subset) +
  scale_fill_continuous(
    low = "white", high = "red", name = "Questions", label = scales::comma
  ) + theme(legend.position = "right") +
    labs(title = paste(category))
  plot
} 

map(vector_of_category, plot_map)

```

Average Response time for each category (bar chart)

```{r}
plot_response <- function(category) {
  subset <- questions %>%
    filter(TakenOnUtc != "NULL" & AskedOnUtc != "NULL" & (category == "" | Category == category)) %>%
    mutate(response_time = as.numeric(difftime(get_time(TakenOnUtc), get_time(AskedOnUtc)))) %>%
    group_by(state) %>%
    summarize(
      values = mean(response_time) / 3600 / 24,
    )
  
  plot_usmap(data = subset) +
    scale_fill_continuous(
      low = "white", high = "red", name = "Average response time (days)", label = scales::comma
    ) + theme(legend.position = "right") +
    labs(title = category)
}

map(vector_of_category, plot_response)
```

Plot of US

```{r}
plot_response("")
```

```{r}
subset <- questions %>%
    filter(TakenOnUtc != "NULL" & AskedOnUtc != "NULL") %>%
    mutate(response_time = as.numeric(difftime(get_time(TakenOnUtc), get_time(AskedOnUtc)))) %>%
    group_by(Category, state) %>%
    summarize(
      values = mean(response_time) / 3600 / 24,
    )

# subsubset <- subset %>%
#   filter(values > 30) %>%
#   write.csv(file = "../../test.csv")

# new_table <- with(subsubset, balloonplot(x = Category, y = state, z = values,
#                   label = FALSE, show.margins = FALSE))
```

```{r}
bad_states <- c("AL", "GA", "SC", "UT")

questions %>%
  filter(state %in% bad_states) %>%
  group_by(AskedOnMonthYear, Category) %>%
  summarize(
    n = n()
  ) %>%
  ggplot(mapping = aes(x = AskedOnMonthYear, y = n, color = Category)) +
  geom_line()
```

```{r}
questions %>%
  filter(state %in% bad_states) %>%
  
```

```{r}
merged_questionposts <- merge(questionpostsprocessed, questions, by = "QuestionUno") %>%
  select(Subcategory, PostTextProcessed) %>%
  write.csv(file = "datasubmerged.csv")
```

```{r}
questions %>%
  group_by(AskedOnMonthYear, Category) %>%
  summarize(
    n = n()
  ) %>%
  write.csv(file = "../../line.csv")
```
